Trajectory model of passive kelp dispersal

### 2020-08-17 thesis_chapter_3.Rmd
added in equations to methods section

## Hydrodynamic drag

The use of shape coefficients was used as a novel approach to simulating biological drifting debris. The drag coefficient for a spherical particle was used in the calculation of hydrodynamic drag as the trajectory model assumes the particles are spherical. The cross-sectional area for each of the virtual kelp parts was determined and used in the calculation of hydrodynamic drag.

>>>>

The energy momemtum equation was used to calculate the drag force exterted on the virtual kelp particle, $$m({d_u/d_t})=F_d + F_w +....$$

The velocity of the virtual kelp float is a combination of the current velocity and the reduction in velocity due to drag such that, $$V = V_c + V_k $$
## Hydrodynamic drag

The use of shape coefficients was used as a novel approach to simulating biological drifting debris. The drag coefficient for a spherical particle was used in the calculation of hydrodynamic drag as the trajectory model assumes the particles are spherical. The cross-sectional area for each of the virtual kelp parts was determined and used in the calculation of hydrodynamic drag. The hydrodynamic/form drag can be calculated by the equation: $$ F_d = 0.5 \rho A_c C_d U^2$$
